---
title: "Homework 10"
author: "Sofia Han (szh247) - SDS 315 UT Austin"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r global_options, echo=FALSE, warning=FALSE}
#Sets the global options
knitr::opts_chunk$set(fig.height=6, fig.width=8, warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))

#Loads the libraries 
suppressMessages(library(tidyverse))
library(rmarkdown)
library(ggplot2)
library(moderndive)
library(effectsize)
suppressMessages(library(mosaic))
suppressMessages(library(kableExtra))
```

**Link to GitHub:** [Click Here](https://github.com/sofiahan/SDS-315-Homework)

***

# **Problem 1: Redlining**

```{r echo=FALSE}
#Imports the dataset
redline <- read.csv("redlining.csv")
```

**Question:** Is there an association between the number of FAIR policies and the racial/ethnic composition of a ZIP code?

**Approach:** To answer the question, I utilized multiple regression that incorporates multiple numerical predictors. I first plotted the overall relationship between minority percentage and number of FAIR policies and fit a model to see what the coefficients were before adjusting for the other variables. I then discretized each of the possible confounding variables into quartiles and plotted the partial relationships with the overall relationship. I then fit a multiple regression model for the number of FAIR policies, using minority, fire, income, and age as variables. Lastly, I computed a 95% confidence interval for each of the coefficients to check for statistical significance. 

**Results:** 

```{r echo=FALSE}
#Plot without adjustment
ggplot(redline, aes(x=minority, y=policies)) +  geom_point() + labs(title = "Overall Relationship Between FAIR Policies and Racial Composition of a ZIP Code", x = "Minority Percentage", y="Number of FAIR Policies (Per 100 Housing Units)") + geom_smooth(method = 'lm')

#Fits the model before adjustment
model1 <- lm(policies~minority, data=redline)
coefficients1 <- coef(model1)
confidence1 <- confint(model1, level = 0.95)

#Creates a nicely formatted table 
kable(coefficients1, col.names = c('Label', 'Value')) %>%
kable_styling(bootstrap_options = c("striped"))
kable(confidence1, col.names = c('Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))
```

Looking at the overall relationship between the number of FAIR policies and minority percentage in the zip code, the number of FAIR policies are expected to increase somewhere between 0.0094 to 0.0182 per 100 housing units in the zip code for every 1% increase in minority percentage in that zip code.

```{r echo=FALSE}
#Stratified by fire
similar_fire <- redline%>%
  mutate(fire_quartile = cut_number(fire, 4))
ggplot(similar_fire, aes(x=minority, y=policies, color = fire_quartile)) + geom_point() + geom_smooth(method='lm') + facet_wrap(~fire_quartile) + geom_abline(intercept = coefficients1[1], slope = coefficients1[2], color = "black")+ labs(title = "FAIR Policies and Racial Composition of a ZIP Code Stratified by Fire Per 100 Housing Units", x = "Minority Percentage", y="Number of FAIR Policies (Per 100 Housing Units)")

#Stratified by age
similar_age <- redline%>%
  mutate(age_quartile = cut_number(age, 4))
ggplot(similar_age, aes(x=minority, y=policies, color = age_quartile)) + geom_point() + geom_smooth(method='lm') + facet_wrap(~age_quartile) + geom_abline(intercept = coefficients1[1], slope = coefficients1[2], color = "black")+ labs(title = "FAIR Policies and Racial Composition of a ZIP Code Stratified by House Age", x = "Minority Percentage", y="Number of FAIR Policies (Per 100 Housing Units)")

#Stratified by income
similar_income <- redline%>%
  mutate(income_quartile = cut_number(income, 4))
ggplot(similar_income, aes(x=minority, y=policies, color = income_quartile)) + geom_point() + geom_smooth(method='lm') + facet_wrap(~income_quartile) + geom_abline(intercept = coefficients1[1], slope = coefficients1[2], color = "black")+ labs(title = "FAIR Policies and Racial Composition of a ZIP Code Stratified by Family Income", x = "Minority Percentage", y="Number of FAIR Policies (Per 100 Housing Units)")
```

When stratified by fire, the slope within each quartile is positive, so when we compare zip codes with similar fire rates, greater minority percentages correlate with a greater number of FAIR policies. The same relationship is observed when stratified by age as well. However, when stratified by income, one of the quartiles actually indicates a negative slope, meaning that when we compare zip codes with median family incomes between 8230 and 10400 dollars, a greater minority percentage correlates with fewer FAIR policies. 

```{r echo = FALSE}
#After adjusting for confounders
model2 <- lm(policies ~ minority + fire + age + income, data = redline)
coefficients2 <- coef(model2)
confidence2 <- confint(model2, level = 0.95)

#Creates a nicely formatted table 
kable(coefficients2, col.names = c('Label', 'Value')) %>%
kable_styling(bootstrap_options = c("striped"))
kable(confidence2, col.names = c('Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))

#get_regression_table(model, conf.level = 0.95)
```

After making the necessary adjustments in the multiple linear regression model, the change in the expected number of FAIR policies for a 1% increase in minority percentage, holding fire, income, and age constant, is still positive, but the coefficient is smaller than that of the unadjusted model. The confidence interval of the minority coefficient did get a bit wider than before, reflecting additional uncertainty. 

**Conclusion:** 

In conclusion, the results indicate that there is an association between the number of FAIR policies and the racial/ethnic composition of a ZIP code as the adjusted multiple regression model indicates a positive coefficient for the minority variable. Additionally, the confidence interval for minority doesn't contain 0, so this positive relationship between FAIR policies and minority percentage is statistically significant at the 0.05 level. 

***

# **Problem 2: Grocery Store Prices**

```{r echo=FALSE}
#Imports the dataset
grocery <- read.csv("groceries.csv")
```

#### Part A: What kind of price differences do we see across the different stores?

```{r echo=FALSE}
#Calculates the average product prices for each store
store_price <- grocery %>%
  group_by(Store)%>%
  summarize(avg_price = mean(Price))

#Creates a bar chart of the above data
ggplot(store_price, aes(x=Store, y = avg_price)) + geom_col() + coord_flip() + labs(title = "Average Price of Products Sold At Stores", x = "Store", y = "Average Price of Products Sold")
```

**Caption:** Based on the bar chart above, the store with products with the greatest average price appears to be Whole Foods at about 4 dollars, and the store with products with the lowest average price appears to be Fiesta at a little over 2 dollars. 

<br>

#### Part B: 

```{r echo=FALSE}
#Counts the number of stores that sell each product
product <- grocery %>%
  group_by(Product)%>%
  summarize(store_count = n())

#Creates a plot of the above data
ggplot(product, aes(x=Product, y=store_count)) + geom_col() + coord_flip() + labs(title = "Number of Stores Selling Each Product", x="Product", y="Number of Stores")
```

**Caption:** Based on the bar graph, the products that are sold in the most number of stores is Horizon 2% Milk and a carton of eggs (16 stores). The products that are sold in the least number of stores are Cinnamon Toast Crunch, El Milagros Tortilla Chips, Frosted Flakes, and Lucky Charms (4 stores).

<br>

#### Part C: Price vs Product and Type

```{r echo=FALSE}
#Fits a model for price vs product and store type
model <- lm(Price ~ Product + Type, data=grocery)
coefficients <- coef(model) %>%
  round(2)
confidence <- confint(model, level = 0.95) %>%
  round(2)

#Creates a nicely formatted table of the confidence interval results
kable(confidence, col.names = c('Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))
```
Compared with ordinary grocery stores, convenience stores charge somewhere between 0.41 to 0.92 dollars more for the same product. 

<br>

#### Part D: Price vs Product and Store

```{r echo=FALSE}
#Fits a model for price vs product and store
model <- lm(Price ~ Product + Store, data = grocery)
coefficients <- coef(model)%>%
  round(2)
confidence <- confint(model, level=0.95)%>%
  round(2)

#Creates a nicely formatted table of the confidence interval results
kable(confidence, col.names = c('Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))
```

**Which two stores seem to charge the lowest prices when comparing the same product?** Walmart and Kroger Fresh Fare

**Which two stores seem to charge the highest prices when comparing the same product?** Whole Foods and Wheatsville Food Co-Op

<br>

#### Part E: HEB and Central Market

```{r echo=FALSE}
#Creates a nicely formatted table of the coefficient results
kable(coefficients, col.names = c('Label', 'Value')) %>%
kable_styling(bootstrap_options = c("striped"))
```
Based on the coefficients from my fitted model, it seems that Central Market charges more than HEB for the same product since HEB charges 0.65 dollars less than the baseline store, holding other variables constant, while Central Market charges 0.57 dollars less than the baseline store, holding other variables constant. The HEB/Central Market difference compared to differences among other stores is relatively moderate. When comparing CVS and Walgreens, which are both drugstores that sell similar products, the price difference is about 0.03, which is smaller than that of Central market and HEB, but when comparing Kroger and Kroger Fresh Fare, which are both Kroger stores, the price difference is about 0.20. Thus, the difference between Central Market and HEB, 0.08, is relatively moderate in comparison. 

<br>

#### Part F: Income

```{r echo=FALSE}
#Creates the income10k variable
new_grocery <- grocery %>%
  mutate(Income10K = Income/10000)

#Fits the model
model <- lm(Price~Product + Income10K, data=new_grocery)
coefficients <- coef(model)%>%
  round(2)
confidence <- confint(model, level=0.95)%>%
  round(2)

#Creates a nicely formatted table of the results
kable(coefficients, col.names = c('Label', 'Value')) %>%
kable_styling(bootstrap_options = c("striped"))
```
Based on the negative sign of the Income10K coefficient, it seems that consumers in poorer ZIP codes seem to pay more for the same product, on average. A coefficient of -0.01 for the Income10K variable means that for every $10,000 increase in income, there is, on average, a decrease of 0.01 in the price of the product, all else being equal. In the context of ZIP codes, this suggests that consumers in wealthier ZIP codes tend to pay slightly less for the same product, on average, compared to consumers in poorer ZIP codes.

```{r echo=FALSE}
#Standardizes the coefficients
standard <- standardize_parameters(model)
one_row <- subset(standard, Parameter == "Income10K")

#Nicely formatted table
kable(one_row, col.names = c('Parameter', 'Standardized Coefficient', 'Confidence Level', 'Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))
```
A one-standard deviation increase in the income of a ZIP code seems to be associated with a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.

<br>