---
title: "Homework 9"
author: "Sofia Han (szh247) - SDS 315 UT Austin"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r global_options, echo=FALSE, warning=FALSE}
#Sets the global options
knitr::opts_chunk$set(fig.height=6, fig.width=8, warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))

#Loads the libraries 
suppressMessages(library(tidyverse))
library(rmarkdown)
library(ggplot2)
library(MatchIt)
suppressMessages(library(mosaic))
suppressMessages(library(kableExtra))
```

**Link to GitHub:** [Click Here](https://github.com/sofiahan/SDS-315-Homework)

***

# **Problem 1: Get Out the Vote**

```{r echo=FALSE}
#Imports the dataset
turnout <- read.csv("turnout.csv")
```

#### Part A (Before Matching): How much more likely are GOTV call recipients to have voted in 1998? 

```{r echo=FALSE}
#Calculates the proportion of those who received a GOTV call and voted in 1998
call <- turnout %>%
  filter(GOTV_call == 1) %>%
  summarize(prop = sum(voted1998 == 1)/n()) %>%
  round(3)

#Creates a nicely formatted table of the proportion
kable(call, col.names = c('Proportion of those who received a GOTV call and voted in 1998')) %>%
kable_styling(bootstrap_options = c("striped"))  
```


```{r echo=FALSE}
#Calculates the proportion of those who didn't receive a GOTV call and voted in 1998
call2 <- turnout %>%
  filter(GOTV_call == 0) %>%
  summarize(prop = sum(voted1998 == 1)/n()) %>%
  round(3)

#Creates a nicely formatted table of the proportion
kable(call2, col.names = c('Proportion of those who did not receive a GOTV call and voted in 1998')) %>%
kable_styling(bootstrap_options = c("striped"))  
```

**Large Sample 95% Confidence Interval for the Difference in the Two Proportions**

```{r echo=FALSE}
#Calculates a large sample 95% confidence interval
test <- prop.test(voted1998==1 ~ GOTV_call, data=turnout)
interval <- test$conf.int
confidence <- tibble("Lower Bound" = interval[1], "Upper Bound" = interval[2])

#Creates a nicely formatted table of the confidence interval results
kable(confidence, col.names = c('Lower Bound', 'Upper Bound')) %>% 
  kable_styling(bootstrap_options = c("striped"))  
```


#### Part B: Confounders

**voted1996**
```{r echo=FALSE}
#Creates a table displaying the relationship between the variables
table1 <- xtabs(~voted1996 + GOTV_call, data = turnout)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table1, col.names = c("Voted in 1996", "Received GOTV Call","Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))

#Creates a table displaying the relationship between the variables
table1 <- xtabs(~voted1996 + voted1998, data = turnout)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table1, col.names = c("Voted in 1996", "Voted in 1998","Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))
```

**AGE**
```{r echo=FALSE}
#Calculates the mean age of each combo
table2 <- mean(AGE~GOTV_call, data=turnout)%>%
  as_tibble()

#Puts them into a tibble
tibble2 <- tibble(
  No = 49.42534,
  yes = 58.30769
)

#Creates a nicely formatted table of the results
kable(tibble2, col.names = c('No GOTV Call', 'Yes GOTV Call')) %>%
kable_styling(bootstrap_options = c("striped"))

#Calculates the mean age of each combo
table2 <- mean(AGE~voted1998, data=turnout)%>%
  as_tibble()

#Puts them into a tibble
tibble2 <- tibble(
  No = 44.91404,
  yes = 55.41535
)

#Creates a nicely formatted table of the results
kable(tibble2, col.names = c('No Vote in 1998', 'Yes Vote in 1998')) %>%
kable_styling(bootstrap_options = c("striped"))
```

**MAJORPTY**
```{r echo=FALSE}
#Creates a table displaying the relationship between the 2 variables
table3 <- xtabs(~MAJORPTY + GOTV_call, data = turnout)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table3, col.names = c("In a Major Party", "Received GOTV Call", "Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))

#Creates a table displaying the relationship between the 2 variables
table3 <- xtabs(~MAJORPTY + voted1998, data = turnout)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table3, col.names = c("In a Major Party", "Voted in 1998", "Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))
```

#### Part C: Matched Data

**Balanced Confounders**

**voted1996**
```{r echo = FALSE}
#Constructs a matched dataset to balance the confounders
turnout_matched <- matchit(GOTV_call ~ voted1996 + AGE + MAJORPTY, data = turnout, ratio = 5) %>%
  match.data

#Checks whether the voted1996 confounder is balanced
table1 <- xtabs(~voted1996 + GOTV_call, data = turnout_matched)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table1, col.names = c("Voted in 1996", "Received GOTV Call", "Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))
```

**AGE**
```{r echo=FALSE}
#Checks whether the age confounder is balanced
table2 <- mean(AGE~GOTV_call, data=turnout_matched)%>%
  as_tibble()

#Puts them into a tibble
tibble2 <- tibble(
  No = 58.26640,
  yes = 58.30769
)

#Creates a nicely formatted table of the results
kable(tibble2, col.names = c('No GOTV Call', 'Yes GOTV Call')) %>%
kable_styling(bootstrap_options = c("striped"))
```

**MAJORPTY**
```{r echo=FALSE}
#Checks whether the majorpty confounder is balanced
table3 <- xtabs(~MAJORPTY + GOTV_call, data = turnout_matched)%>%
  prop.table(margin = 2)%>%
  as_tibble()

#Creates a nicely formatted table of the results
kable(table3, col.names = c("In a Major Party", "Received GOTV Call", "Proportion"))%>%
  kable_styling(bootstrap_options = c("striped"))
```


```{r echo=FALSE}
#Calculates the proportion of those who received a GOTV call and voted in 1998
call <- turnout_matched %>%
  filter(GOTV_call == 1) %>%
  summarize(prop = sum(voted1998 == 1)/n()) %>%
  round(3)

#Creates a nicely formatted table of the proportion
kable(call, col.names = c('Proportion of those who received a GOTV call and voted in 1998')) %>%
kable_styling(bootstrap_options = c("striped"))  
```


```{r echo=FALSE}
#Calculates the proportion of those who didn't receive a GOTV call and voted in 1998
call2 <- turnout_matched %>%
  filter(GOTV_call == 0) %>%
  summarize(prop = sum(voted1998 == 1)/n()) %>%
  round(3)

#Creates a nicely formatted table of the proportion
kable(call2, col.names = c('Proportion of those who did not receive a GOTV call and voted in 1998')) %>%
kable_styling(bootstrap_options = c("striped"))  
```

**Large Sample 95% Confidence Interval for the Difference in the Two Proportions**

```{r echo=FALSE}
#Calculates a large sample 95% confidence interval
test <- prop.test(voted1998==1 ~ GOTV_call, data=turnout_matched)
interval <- test$conf.int
confidence <- tibble("Lower Bound" = interval[1], "Upper Bound" = interval[2])

#Creates a nicely formatted table of the confidence interval results
kable(confidence, col.names = c('Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))  
```

**What do you conclude about the overall effect of the GOTV call on the likelihood of voting in the 1998 election?**

**Response:** From the confidence interval results, I can say with 95% confidence that those who received a GOTV call had a higher proportion of voting in 1998 compared to those who did not receive a GOTV call, on average, with a difference in proportions somewhere between -0.1417567 and -0.0056117. Additionally, since this confidence interval does not include 0, the difference is statistically significant at the 5% level. In conclusion, the GOTV call had a statistically significant positive effect on the likelihood of voting in the 1998 election, with the group who received the GOTV call being more likely to vote compared to those who didn't receive it.

<br>

# **Problem 2: Manufacturing Flaws in Circuit Boards**

```{r echo=FALSE}
#Imports the dataset
solder <- read.csv("solder.csv")
```

#### Part A: Plots

```{r echo=FALSE}
#Creates a boxplot of size of gun opening and skips
ggplot(solder, aes(x = Opening, y = skips)) + geom_boxplot() + labs(title = "Relationship Between Opening Size and Skips", x = "Size of Opening on Solder Gun", y = "Number of Skips")
```

**Caption:** Based on the plot, it seems that as the size of the opening on the solder gun becomes smaller, the median number of skips increases. Furthermore, as the size of the opening on the solder gun increases, the data becomes more spread out, indicating more variability. 

```{r echo=FALSE}
#Creates a boxplot of alloy thickness and skips
ggplot(solder, aes(x = Solder, y = skips)) + geom_boxplot() + labs(title = "Relationship Between Alloy Thickness and Skips", x = "Thickness of Solder Alloy", y = "Number of Skips")
```

**Caption:** Based on the plot, the median number of skips for the thin solder alloy is greater than that of the thick solder alloy. Additionally, the data for the thin solder alloy has more variability than that of the thick solder alloy. 


#### Part B: Regression Model

```{r echo=FALSE}
#Builds a regression model with skips as the outcome variable
model <- lm(skips ~ Opening + Solder + Opening:Solder, data=solder)
coefficients <- coef(model) %>%
  round(3)

#Creates a nicely formatted table of the coefficients
kable(coefficients, col.names = c('Label','Value')) %>%
kable_styling(bootstrap_options = c("striped"))

#Creates a confidence interval for the coefficients in the model
confidence <- confint(model, level = 0.95) %>% 
  round(3)

#Creates a nicely formatted table of the confidence interval results
kable(confidence, col.names = c('Value', 'Lower Bound', 'Upper Bound')) %>%
kable_styling(bootstrap_options = c("striped"))
```

#### Part C: Interpretation

**Intercept:** The baseline number of solder skips when the opening size is large and the solder thickness is thick is about 0.393.

**OpeningM:** On average, when the opening size of the solder gun is medium instead of large (the baseline), we expect an increase of approximately 2.407 solder skips, holding other variables constant.

**OpeningS:** Compared to the baseline level of large opening size, when the opening size is small, we anticipate approximately 5.127 additional solder skips, holding other variables constant.

**SolderThin:** Holding other variables constant, when the solder type is thin instead of thick (the baseline level), we expect an increase of approximately 2.280 solder skips on average.

**OpeningM:SolderThin** When the solder type is thin and the opening size is medium, there are approximately 0.740 fewer solder skips on average than what one would expect from summing the individual isolated effects of the two variables.

**OpeningS:SolderThin** When the solder type is thin and the opening size is small, there are approximately 9.653 more solder skips on average than what one would expect from summing the individual isolated effects of the two variables.



#### Part D: 

**If you had to recommend a combination of Opening size and Solder thickness to AT&T based on this analysis, which one would it be, and why?**

**Response:** I would recommend a combination of opening size M and thin solder thickness to AT&T based on this analysis because the interaction effect for that combination resulted in less solder skips as the estimated coefficient was negative while the other effects resulted in more solder skips as they all had positive estimated coefficients. 



<br>